---
title: "Search Name Segmentation Criteria and New Estimate"
author: "Office of Marketing and Brand Management"
date: "2/10/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

# Geographic Markets

## Primary Market

**Maine**

* All Counties

## Secondary Markets

**Massachusetts**

* Middlesex County

**New Hampshire**

* Hillsborough County

* Rockingham County

* Strafford County


## Tertiary Markets

**Massachusetts**

* All Other Counties

**New Hampshire**

* All Other Counties

**Connecticut**

* All Counties

## Quaternary Markets

**Vermont**

* All Counties

**Rhode Island**

* All Counties

**Outside of New England**

**New York** 

* Westchester

# GPA

## High Achievers

* GPA between 4.00 and 3.70 

* Letter grade between A+ and A-

## General Achievers

* GPA between  3.6 and 2.7

* Letter grade between B+ and B-

## Aspirational Achievers (modify for primary market, all grades C+ and less)

* GPA between 2.6 and 2.3

* Letter grade of C+


#  Standardized Test Scores (not for primary market)

* SAT test takers with scores between 800 – 1400

* PSAT test takers with scores between 720 – 1520

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(kableExtra)
```

# Junior Names Available as of February 10, 2020


```{r echo=FALSE}
data <- read.csv("C:/Users/christine.iyer/Box/Search Name Evaluation/Search Infrmation/Junior_Search_Name_Availability_Feb_10_20.csv", header = T, stringsAsFactors = F)
data %>% kable() %>% kable_styling()
```


